Testing Data from the Toronto Paramedic Service

### 2023-02-03 scripts/03-data_testing.qmd
General cleaning and adding comments
* Added a note to the incident data testing to describe an issue where the test returns two Booleans, one of which is false. Clarified this incident for the user.
* Fixed minor spacing issue with paper.qmd

# Test that the incident type contains is comprised of characters
clean_incident_data$incident_type |> class() == "character"
```

>>>>

# Test that the incident type contains is comprised of characters
clean_incident_data$incident_type |> class() == "character"

# Note: due to an issue with the dispatch_time's column formatting as a date,
# the second returned Boolean may be false. As long as the first value returns 
# true, the data passes the test.
```
